Subsegmental language detection in Celtic language text

### 2014-06-28 codeswitch-cltw-2014/codeswitch_camera_ready.tex
more changes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55057 72bbbca6-d526-0410-a7d9-f06f51895060
more changes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55060 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

There are several ways in which an informal text may contain parts in different languages, such as
code switching, quotations, named entities, interjections, translations --- either of the full text, or 
part of the text, comments, etc. Some of these are presented in Table~\ref{table:examples}.

@@

@@

This section describes the heuristics taken into account while performing the chunking of the input data according to 
the sequences of segments in different languages. 
'Chunks' represent the evaluated tuples of segments and their labelled language, buffer is the expanding segment.
 \textit{lang\_predict} corressponds to any function which is used to determine the language of the token. The flag 
variable helps in implementing the heuristic of minimum segment size while labelling chunks.

\begin{algorithm}
\caption{Chunking algorithm}\label{euclid}
\begin{algorithmic}[1]
%\Procedure{}{}
\State $\textit{buffer} = [\ ] \text{\ \ \  \#undecided expanding window of chunk}$
\State $\textit{chunks} = [\ ] \text{\ \ \  \#decided labelled segment}$
\State $\textit{buffer\_language} \gets \textit{lang\_predict}\text{(sentence[0])} \text{\ \ \ \#Language of first word}$
\State $\textit{flag} \gets \text{0}$
%\State $\text{for \ } \textit{word \ } \text{in \ } \textit{sentence:} $
\For{\texttt{word in sentence}}
\If {$ \textit{lang\_predict(word)} \text{==} \textit{buffer\_language} $}
        \If {$ \textit{flag} \text{=\ =\ 1} $}
        \State $\textit{buffer} += [\textit{word\_d,word}] $
        \State $\textit{flag} \gets \text{0}$
        \Else
        \State $\textit{buffer} += [\textit{word}] $
        \EndIf
        \EndIf
\If {$ \textit{lang\_prediction(word)} \text{!=} \textit{buffer\_langugae} $}
        \If {$ \textit{flag} \text{=\ =\ 0} $}
        \State $\textit{flag} \gets \text{1}$
        \State $\textit{word\_d} \gets \textit{word} $
        \State $\text{continue}$

        \Else
        \State $\textit{chunk} \text{+= \ }  \textit{[(buffer,buffer\_language)]} $
        %\State $\textit{buffer} \gets [] $
        \State $\textit{buffer} = [\textit{word\_d,word}] $
        \State $\textit{buffer\_language} = \gets \textit{lang\_predict}\text{(word)}$% \text{\#Language of new expanding chunk}$
        \State $\textit{flag} \gets \text{0}$
        \EndIf

\EndIf
\EndFor
\If {$\textit{length(buffer)} \text{!=0\ } $}
        \State $\textit{chunk} \text{+= \ }  \text{[\textit{[(buffer,buffer\_language)]}} $

\EndIf
%\EndProcedure
\end{algorithmic}
\end{algorithm}

%A flag is set at the beginning of the input text, and this moves forward to the position in the text upto where confident 
%chunking has been performed. For example, in case of a continuous prediction there would be no change and since the 
%predicted tag of the new word corresponds to that already of the expanding chunk, this word is also included in the 
%same chunk. In case of a doubt, the flag is set at the same position, and no final decision on labelling the word is 
%performed, to have more confidence on the code-switch, the process moves on to the next token, if it corresponds to 
%that of the previous chunk, then both these undecided words are labelled and included in the chunk, otherwise a change 
%is noted and a new chunk is created with the changed label. In this process, we are trying to identify the sub-segments 
%that we need, thus performing both tasks at once, the first being language prediction and second being the chunking decision.

\subsection{Word-based prediction}
\label{wbased}

@@

@@

For our current task, each of the texts have been limited to two languages i.e. the primary language (the Celtic language) and the 
secondary language (the `majority' language). Hence the type of chunking tags are limited to these. The evaluation statistics shown 
in Tables~\ref{table:precisionrecall}~and~\ref{table:accuracy} mention two values for each of the experiment conducted on the three bilingual 
language datasets. The first, is the percentage of correctly detected phrases, which is the overall precision and the second is the 
number of phrases in the data that were found by the chunker, which is the overall recall. \\

>>>>

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algcompatible}
\usepackage[noend]{algpseudocode}

@@

%Such as
%code switching, quotations, named entities, interjections, translations --- either of the full text, or 
%part of the text, comments, etc.

@@

There are several ways in which an informal text may contain parts in different languages.
Some of these are presented in Table~\ref{table:examples}.

@@

This section describes the heuristics taken into account while performing the chunking of the input data according to 
the sequences of segments in different languages. 
In Figure ~\ref{fig:chunkal}, `chunks' represent the list of evaluated tuples of segments and their labelled language, `buffer' is the expanding segment.
 \textit{lang\_predict} corressponds to any function which is used to determine the language of the token. The flag 
variable helps in implementing the heuristic of minimum segment size while labelling chunks.
\begin{algorithm}
\caption*{\textsc{}}
%\caption{Chunking algorithm}\label{euclid}
{\fontsize{10}{10}\selectfont
\begin{algorithmic}[1]
%\Statex{}%Procedure{}{}
\Statex $\textit{buffer} = [\ ] \text{\ \ \  \#undecided expanding window of chunk}$
\Statex $\textit{chunks} = [\ ] \text{\ \ \  \#decided labelled segment}$
\Statex $\textit{buffer\_language} \gets \textit{lang\_predict}\text{(sentence[0])} \text{\ \ \ \#Language of first word}$
\Statex $\textit{flag} \gets \text{0}$
%\State $\text{for \ } \textit{word \ } \text{in \ } \textit{sentence:} $
\For{\texttt{word in sentence}}
\If {$ \textit{lang\_predict(word)} \text{==} \textit{buffer\_language} $}
        \If {$ \textit{flag} \text{=\ =\ 1} $}
        \Statex $\textit{buffer} += [\textit{word\_d,word}] $
        \Statex $\textit{flag} \gets \text{0}$
        \Else
        \Statex $\textit{buffer} += [\textit{word}] $
        \EndIf
        \EndIf
\If {$ \textit{lang\_prediction(word)} \text{!=} \textit{buffer\_langugae} $}
        \If {$ \textit{flag} \text{=\ =\ 0} $}
        \Statex $\textit{flag} \gets \text{1}$
        \Statex $\textit{word\_d} \gets \textit{word} $
        \Statex $\text{continue}$

        \Else
        \Statex $\textit{chunk} \text{+= \ }  \textit{[(buffer,buffer\_language)]} $
        %\State $\textit{buffer} \gets [] $
        \Statex $\textit{buffer} = [\textit{word\_d,word}] $
        \Statex $\textit{buffer\_language} = \gets \textit{lang\_predict}\text{(word)}$% \text{\#Language of new expanding chunk}$
        \Statex $\textit{flag} \gets \text{0}$
        \EndIf

\EndIf
\EndFor
\If {$\textit{length(buffer)} \text{!=0\ } $}
        \Statex $\textit{chunk} \text{+= \ }  \text{[\textit{[(buffer,buffer\_language)]}} $

\EndIf
%\EndProcedure
%\Statex{}
\end{algorithmic}}
\end{algorithm}
\vspace{-0.4cm}
\begin{figure}[hb]
\def\@fs@post{}
\caption{Chunking Algorithm}
\label{fig:chunkal}
\end{figure}
%A flag is set at the beginning of the input text, and this moves forward to the position in the text upto where confident 
%chunking has been performed. For example, in case of a continuous prediction there would be no change and since the 
%predicted tag of the new word corresponds to that already of the expanding chunk, this word is also included in the 
%same chunk. In case of a doubt, the flag is set at the same position, and no final decision on labelling the word is 
%performed, to have more confidence on the code-switch, the process moves on to the next token, if it corresponds to 
%that of the previous chunk, then both these undecided words are labelled and included in the chunk, otherwise a change 
%is noted and a new chunk is created with the changed label. In this process, we are trying to identify the sub-segments 
%that we need, thus performing both tasks at once, the first being language prediction and second being the chunking decision.

\vspace{-0.6cm}
\subsection{Word-based prediction}
\label{wbased}

@@

\vspace{-0.4cm}

@@

For our current task, each of the texts have been limited to two languages i.e. the primary language (the Celtic language) and the 
secondary language (the `majority' language). Hence the type of chunking tags are limited to these. The evaluation statistics shown 
in Tables~\ref{table:precisionrecall}~and~\ref{table:accuracy} mention two values for each of the experiment conducted on the three bilingual 
language datasets. The first, is the percentage of correctly detected phrases, which is the overall precision and the second is the 
number of phrases in the data that were found by the chunker, which is the overall recall.
